A parametric system for generating contour parallel toolpaths with adaptive extrusion width

### 2019-08-23 4_method.tex
lil rewording

\subsubsection{Medial axis transform}
One of the most commonly used skeletonizations of a shape is the medial axis.
The medial axis is defined by the locations where the inscribed circle meets the boundary in at least two locations. \cite{blum1967transformation}
We call the set of closest points on the outline polygon $P$ of a point $v$ on the skeleton its \emph{support}: $\text{sup}(v) = \argmin_{x\in P} |x - v|$.
The resulting skeleton consists of straight segments and parabolic segments which form a graph.
See \cref{MAT_explanation_circles}.

@@

\begin{figure}\centering
\setlength{\figwidth}{0.19\columnwidth}
\setlength{\figwidthTwo}{0.3\columnwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_mat}
\caption{Medial Axis}\label{shape_decomposition_mat}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_vd}
\caption{Voronoi Diagram}\label{shape_decomposition_vd}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_st}
\caption{Skeletal Trapezoids}\label{shape_decomposition_st}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/half_edge_datastructure.pdf}
\caption{Data structure}\label{shape_decomposition_datastructure}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/domains.pdf}
\caption{Polygon Domains}\label{shape_decomposition_domains}
\end{subfigure}
\caption{
Skeletonization of an outline shape (black).
Relation between the medial axis (red), the limited Voronoi Diagram (red and green) and the Skeletal Trapezoidation (red, green and gray): MAT $\subset$ Limited VD $\subset$ ST.
}
\label{skeletonization_comparison}
\end{figure}

\subsubsection{Skeletal trapezoidation}
The MAT decomposes the outline shape into several complex shapes which we need to further decompose in order to have a mesh consisting only of quads and triangles.
We employ a shape decomposition proposed by \citeauthor{Ding2016a}. \cite{Ding2016a}
Each of the regions demarcated by the skeleton is further decomposed by adding radial bones from each node $v$ to its support $\text{sup}(v)$.
The resulting skeleton decomposes the outline shape into trapezoids and triangles.
We will therefore call this shape decomposition the \emph{Skeletal Trapezoidation} (ST).
(The concept of a trapezoidation conventionally allows for the degenerate case where a trapezoid resolves into a triangle. \cite{chazelle1984,fournier1984})
We represent such a skeleton in a standard half-edge data-structure.
See \cref{shape_decomposition_datastructure}.

@@

We then also discretize parabolic segments and segments generated by two concave outline vertices into segments approximately as long as some constant $d^\text{discretization}$.
See \cref{discretization} and the middle of \cref{shape_decomposition_st}.
That way we can approximate the feature radius $R$ in between the two nodes $v_0$ and $v_1$ of a bone in the ST by interpolating linearly between $R(v_0)$ and $R(v_1)$.
This makes the skeleton capture a discrete approximation of the radius function which is then used to determine the height of each node in the skeleton in order to generate the 3D mesh of the UoC.
The UoC is the ST along with the corresponding feature radius $R$ as the height of each node.
%; see \cref{mat_3d}.

\subsubsection{Union of cones}
In order to transform the ST into a 3D surface we add another dimension to the skeleton.
We assign each node a height value measured in terms of an integer number: it's \emph{bead count}.
We define the bead count as the number of beads to fit along the \emph{diameter} of the shape, which is twice the feature radius.
While the feature radii are measured along the support bones, the diameter is not measurable as such because the support bones are generally not collinear;
we introduce the concept of the diameter so that we can deal with an odd number of beads while using integer logic.

>>>>

\subsubsection{Medial axis transform}
One of the most commonly used skeletonizations of a shape is the medial axis.
The medial axis is defined by the locations where the inscribed circle meets the boundary in at least two locations. \cite{blum1967transformation}
We call the set of closest points on the outline polygon $P$ of a point $v$ on the skeleton its \emph{support}: $\text{sup}(v) = \argmin_{x\in P} |x - v|$.
The resulting skeleton consists of straight segments and parabolic segments which form a graph.
See \cref{MAT_explanation_circles}.
We therefore represent the skeleton in a standard half-edge data-structure.
See \cref{shape_decomposition_datastructure}.

@@

\begin{figure}\centering
\setlength{\figwidth}{0.19\columnwidth}
\setlength{\figwidthTwo}{0.3\columnwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_mat}
\caption{Medial Axis}\label{shape_decomposition_mat}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_vd}
\caption{Voronoi Diagram}\label{shape_decomposition_vd}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_st}
\caption{Skeletal Trapezoids}\label{shape_decomposition_st}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/half_edge_datastructure.pdf}
\caption{Data structure}\label{shape_decomposition_datastructure}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/domains.pdf}
\caption{Polygon Domains}\label{shape_decomposition_domains}
\end{subfigure}
\caption{
Skeletonization of an outline shape (black).
Relation between the medial axis (red), the limited Voronoi Diagram (red and green) and the Skeletal Trapezoidation (red, green and gray): MAT $\subset$ Limited VD $\subset$ ST.
\subref{shape_decomposition_datastructure} We can represent a skeleton using a half-edge data-structure.
\subref{shape_decomposition_domains} The ST divides the shape into primitives which can be classified as belonging to one of the inout shape polygons.
}
\label{skeletonization_comparison}
\end{figure}

\subsubsection{Skeletal trapezoidation}
The MAT decomposes the outline shape into several complex shapes which we need to further decompose in order to have a mesh consisting only of quads and triangles.
We employ a shape decomposition proposed by \citeauthor{Ding2016a}. \cite{Ding2016a}
Each of the regions demarcated by the skeleton is further decomposed by adding radial bones from each node $v$ to its support $\text{sup}(v)$.
The resulting skeleton decomposes the outline shape into trapezoids and triangles.
We will therefore call this shape decomposition the \emph{Skeletal Trapezoidation} (ST).
\footnote{The concept of a trapezoidation conventionally allows for the degenerate case where a trapezoid resolves into a triangle. \cite{chazelle1984,fournier1984}}

@@

We then also discretize parabolic segments and segments generated by two concave outline vertices into segments approximately as long as some constant $d^\text{discretization}$.
See \cref{discretization} and the middle of \cref{shape_decomposition_st}.
That way we can approximate the feature radius $R$ in between the two nodes $v_0$ and $v_1$ of a bone in the ST by interpolating linearly between $R(v_0)$ and $R(v_1)$.
This makes the ST capture a discrete approximation of the radius function which is then used to determine the height of each node in the skeleton in order to generate the 3D mesh of the UoC.
%; see \cref{mat_3d}.

\subsubsection{Union of cones}
In order to visualize the ST as a 3D surface, we add a third dimension.
We assign each node a height value measured in terms of beads: it's \emph{bead count}.
We define the bead count as the number of beads to fit along the \emph{diameter} of the shape, which is twice the feature radius.
While the feature radii are measured along the support bones, the diameter is not measurable as such because the support bones are generally not collinear;
we introduce the concept of the diameter so that we can deal with an odd number of beads while using integer logic.
